Clustering of Distributions on 1-Dimensional Manifolds

### 2021-09-01 scratch/distributions-on-1d-manifolds.tex
proof sketch for general case

\hypertarget{beta-case}{%
\subsubsection{Beta case}\label{beta-case}}

@@

@@

Which becomes \(1 - C P(n) e^{-n}\) for some \(C > 0\) and \(P(n)\) is a
polynomial of \(n\). This goes to 0 as \(n \to \infty\), giving us the
result \(D_i \stackrel{p}{\to} 0\).

>>>>

@@

\hypertarget{proof-sketch-that-pd_i-leq-delta-to-1}{%
\paragraph{\texorpdfstring{Proof sketch that
\(P(D_i \leq \delta) \to 1\)}{Proof sketch that P(D\_i \textbackslash leq \textbackslash delta) \textbackslash to 1}}\label{proof-sketch-that-pd_i-leq-delta-to-1}}

@@

Which becomes \(1 - C P(n) \delta^{n}\) for some \(C > 0\) and \(P(n)\)
is a polynomial of \(n\). This goes to 0 as \(n \to \infty\), giving us
the result \(D_i \stackrel{p}{\to} 0\).
